---
title: "BioRad Vertical Profiles"
output: 
    flexdashboard::flex_dashboard:
      vertical_layout: scroll
      orientation: rows
      theme: yeti
social: menu
source_code: embed
runtime: shiny
---
    
```{r global, include=FALSE}

# load data in 'global' chunk so it can be shared by all users of the dashboard
source('lib/initialize.R')
station_choices <- read_csv(here('nexrad_station_info/nexrad-stations.csv'))
bioRad::check_docker()


```

Instructions
=======================================================================

### Welcome
This is a flexDashboard that was built around the BioRad package's `calculate_vp()` function. It's purpose is to take some of the hassle and potential for error out of the process by replacing code inputs with a graphical user interface. 

Documentation for the `bioRad::calculate_vp()` function may be found here:

* https://rdrr.io/cran/bioRad/man/calculate_vp.html


When you are ready to begin, click the tab at the top labeled "Calculate Vertical Profiles."

Once there, select a NEXRAD station from the available choices to the left. Next, select the date that you are interested in. A drop down list will show the available NEXRAD files for the selected station and date. Select a file and decide whether or not you want to rely on Automatic Configuration. If manual configuration is required, remove the checkbox from the Enable Automatic Configuration option. Adjust the parameters to your liking. In both automatic and manual mode, clicking "Calculate Vertical Profile" will begin calculations

Tabs will populate to the right with a plot and tabular information about the selected date and time. Each can be saved to your machine as a PNG or CSV/EXCEL file respectively. 

Have fun!

Calculate Vertical Profiles
=======================================================================

Inputs {.sidebar data-width=400}
-----------------------------------------------------------------------
    
```{r}
# Select NEXRAD Station
selectInput(inputId = 'nex_station', label = strong('Select NEXRAD Station:'), width = '100%',
              choices = station_choices %>% 
                select(ICAO) %>%
                distinct() %>% 
                deframe(),
              selected = 'KFWS')
# Select Date
dateInput(inputId = 'date', label = strong('Select Date:'), width = '100%')

# Create a list of available NEXRAD files for selected station and date
available_files <- reactive({
    get_bucket_df(bucket = "noaa-nexrad-level2", 
                  key = "",
                  prefix = paste0(as.character(input$date, format="%Y/%m/%d"),"/", input$nex_station)
                  ) %>% 
        tibble()
    })
# Select NEXRAD file
renderUI({
    selectInput(inputId = 'nex_file', 
                label = strong('Select from Available NEXRAD Files:'), 
                width = '100%',
                choices = available_files() %>% 
                  deframe()
                )
  })
# autoconfig
checkboxInput(inputId = 'autoconf',
              label = tagList(strong('Enable Automatic Configuration?'),
                              br(),
                              tags$sub('logical. When TRUE, default optimal configuration settings are selected automatically, and other user settings are ignored.'),
                              br(),
                              tags$sub('Turn on autoconf to automatically select the optimal parameters for a given radar file. The default for C-band data is to apply rain-filtering in single polarization mode, as well as dual polarization mode when available.'),
                              br(),
                              tags$sub('The default for S-band data is to apply precipitation filtering in dual-polarization mode.')
                              ),
              value = TRUE,
              width = '100%')

# Create GUI components for all calculate_vp toggles/switches
# nyquist_min
nyquist_min <- reactive({
  ifelse(input$dealias == T, 5, 25)
})
output$nyquist_min_ui <- renderUI({tagList(strong('nyquist_min'),
                                            br(),
                                            renderText(nyquist_min() ),
                                            tags$sub('numeric. Minimum Nyquist velocity of scans in m/s for scans to be included in the analysis.')
                                            )
                                    })
renderUI({
  if(input$autoconf == FALSE) {
  tagList(
# sd_vpp_threshold
numericInput(inputId = 'sd_vpp_threshold', 
             label = tagList(strong('sd_vpp_threshold'), 
                             br(),
                             tags$sub('numeric. Lower threshold in radial velocity standard deviation (profile quantity sd_vvp) in m/s. Biological signals with sd_vvp < sd_vvp_threshold are set to zero.')
                             ),
             value = 1,
             width = '100%'),

# rcs
numericInput(inputId = 'rcs', 
             label = tagList(strong('rcs'), 
                             br(),
                             tags$sub('numeric. Radar cross section per bird in cm^2.')
                             ),
             value = 11,
             width = '100%'),

# dual_pol
checkboxInput(inputId = 'dual_pol',
              label = tagList(strong('Use dual-pol mode?'),
                              br(),
                              tags$sub('logical. When TRUE use dual-pol mode, in which meteorological echoes are filtered using the correlation coefficient rho_hv. When FALSE use single polarization mode based only on reflectivity and radial velocity quantities.')),
              value = TRUE),

# rho_hv
numericInput(inputId = 'rho_hv', 
             label = tagList(strong('rho_hv'), 
                             br(),
                             tags$sub('numeric. Lower threshold in correlation coefficient used to filter meteorological scattering.')
                             ),
             value = 0.95,
             min = 0,
             max = 1,
             step = 0.01, 
             width = '100%'),

# elev_min
numericInput(inputId = 'elev_min', 
             label = tagList(strong('elev_min'), 
                             br(),
                             tags$sub('numeric. Minimum scan elevation in degrees.')
                             ),
             value = 0,
             min = 0,
             max = 90,
             step = 1,
             width = '100%'),

# elev_max
numericInput(inputId = 'elev_max', 
             label = tagList(strong('elev_max'), 
                             br(),
                             tags$sub('numeric. Maximum scan elevation in degrees.')
                             ),
             value = 90,
             min = 1,
             max = 90,
             step = 1,
             width = '100%'),

# azim_min
numericInput(inputId = 'azim_min', 
             label = tagList(strong('azim_min'), 
                             br(),
                             tags$sub('numeric. Minimum azimuth in degrees clockwise from north.')
                             ),
             value = 0,
             min = 0,
             max = 360,
             step = 0.5,
             width = '100%'),

# azim_max
numericInput(inputId = 'azim_max', 
             label = tagList(strong('azim_max'), 
                             br(),
                             tags$sub('numeric. Maximum azimuth in degrees clockwise from north.')
                             ),
             value = 360,
             min = 1,
             max = 360,
             step = 0.5,
             width = '100%'),

# min max range
sliderInput(inputId = 'min_max_range',
            label = tagList(strong('Minimum and Maximum Range (km)'),
                            br(),
                            tags$sub('numeric. Minimum and maximum range in km.')
                            ),
            min = 0,
            max = 230,
            value = c(5,35),
            step = 1,
            width = '100%'),

# n_layer
sliderInput(inputId = 'n_layer', 
            label = tagList(strong('n_layer'), 
                            br(),
                            tags$sub('numeric. Number of altitude layers in the profile.')
                            ),
             value = 20,
             min = 1,
             max = 100,
             step = 1,
             width = '100%'),

# h_layer
numericInput(inputId = 'h_layer', 
             label = tagList(strong('h_layer'), 
                             br(),
                             tags$sub('numeric. Width of altitude layers in meters.')
                             ),
             value = 200,
             min = 100,
             max = 2000,
             step = 100,
             width = '100%'),

# dealias
checkboxInput(inputId = 'dealias',
              label = tagList(strong('Dealias radial velocities?'),
                              br(),
                              tags$sub('logical. Whether to dealias radial velocities; this should typically be done when the scans in the polar volume have low Nyquist velocities (below 25 m/s).')),
              value = TRUE),

uiOutput('nyquist_min_ui'),

# dbz_quantity
selectInput(inputId = 'dbz_quantity',
            label = tagList(strong('dbz_quantity'),
                            br(),
                            tags$sub('character. One of the available reflectivity factor quantities in the ODIM radar data format, e.g. DBZH, DBZV, TH, TV.')
                            ),
            choices = c('DBZH','DBZV','TH','TV'),
            selected = 'DBZH',
            multiple = F,width = '100%')
)
  } else{return(NULL)}
})

actionButton(inputId = 'action',label = 'Calculate Vertical Profile',icon = icon('satellite-dish'))

```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Vertical Profile

```{r, fig.height=10, fig.width=8}

# Download radar data and store vertical profile information as a reactive variable when button clicked
  my_vp <- eventReactive(input$action, {
    # Check to see if you already have the radar file, if so, use it
    if(file.exists(here('nexrad_data', input$nex_file)) == T & input$autoconf == F) {
      # Using BioRad, calculate vertical profile
      calculate_vp(here('nexrad_data', input$nex_file),
                   sd_vvp_threshold = input$sd_vpp_threshold,
                   rcs = input$rcs,
                   dual_pol = input$dual_pol,
                   rho_hv = input$rho_hv,
                   elev_min = input$elev_min,
                   elev_max = input$elev_max,
                   azim_min = input$azim_min,
                   azim_max = input$azim_max,
                   range_min = input$min_max_range[1]*1000, #data entry in kilometers, function expects meters
                   range_max = input$min_max_range[2]*1000, #data entry in kilometers, function expects meters
                   n_layer = input$n_layer,
                   h_layer = input$h_layer,
                   dealias = input$dealias,
                   nyquist_min = nyquist_min(),
                   dbz_quantity = input$dbz_quantity)
    } else if (file.exists(here('nexrad_data', input$nex_file)) == F & input$autoconf == F) {
    # If you don't already have the necessary file...
    # Save Radar Data File from AWS
      save_object(object = input$nex_file, bucket = "noaa-nexrad-level2", key = "", secret = "", region = "us-east-1",
                      file = here('nexrad_data', input$nex_file))
    # Using BioRad, calculate vertical profile
      calculate_vp(here('nexrad_data', input$nex_file),
                   sd_vvp_threshold = input$sd_vpp_threshold,
                   rcs = input$rcs,
                   dual_pol = input$dual_pol,
                   rho_hv = input$rho_hv,
                   elev_min = input$elev_min,
                   elev_max = input$elev_max,
                   azim_min = input$azim_min,
                   azim_max = input$azim_max,
                   range_min = input$min_max_range[1]*1000, #data entry in kilometers, function expects meters
                   range_max = input$min_max_range[2]*1000, #data entry in kilometers, function expects meters
                   n_layer = input$n_layer,
                   h_layer = input$h_layer,
                   dealias = input$dealias,
                   nyquist_min = nyquist_min(),
                   dbz_quantity = input$dbz_quantity)
    } else if (file.exists(here('nexrad_data', input$nex_file)) == T & input$autoconf == T) {
      # Using BioRad, calculate vertical profile
      calculate_vp(here('nexrad_data', input$nex_file),
                   autoconf = input$autoconf)
    } else {
      # If you don't already have the necessary file...
    # Save Radar Data File from AWS
      save_object(object = input$nex_file, bucket = "noaa-nexrad-level2", key = "", secret = "", region = "us-east-1",
                      file = here('nexrad_data', input$nex_file))
    # Using BioRad, calculate vertical profile
      calculate_vp(here('nexrad_data', input$nex_file),
                   autoconf = input$autoconf)
    }
      })
# Offer an option to save the plot
plot_filename <- eventReactive(input$action, {
  ifelse(input$autoconf == T, paste0('automatic_options_',basename(input$nex_file), ".png"), paste0('manual_options_',basename(input$nex_file), ".png") )
})
plot_title <- eventReactive(input$action, {
    ifelse(input$autoconf == T, paste0('automatic_options_',basename(input$nex_file)), paste0('manual_options_',basename(input$nex_file)) )

})
# downloadButton(outputId = "savePlot",label = "Save Plot")
  downloadHandler(filename = function() {
    filename = plot_filename()
    },
    content = function(file) {
      png(file, width = 640, height = 480)
      plot(my_vp(), quantity = 'dbz',main = plot_title() ) 
      dev.off()
      }
    )
# Render the Vertical Profile
  miniContentPanel(
  renderPlot({
    req(my_vp() )
    plot(my_vp(), quantity = 'dbz',main = plot_title() ) 
    }, height = 750),
  scrollable = T
  )
```

### Tabular
```{r}
tabular_filename <- reactive({
      ifelse(input$autoconf == T, paste0('automatic_options_',basename(input$nex_file)), paste0('manual_options_',basename(input$nex_file)) )
  })
renderDataTable({
  req(my_vp())
  my_vp()$data %>% 
    datatable(extensions = list('Scroller' = NULL,'Buttons' = NULL),
              options = list(scrollX = TRUE,
                 deferRender = TRUE,
                 scrollY = '600px',
                 scroller = TRUE,
                 searchHighlight = TRUE, 
                 search = list(regex = TRUE, 
                               caseInsensitive = TRUE),
                 dom = 'Bfrtip',
                 buttons = list(list(extend = 'csv',
                                     filename = tabular_filename()),
                                list(extend= 'excel',
                                     filename = tabular_filename())
                                )
                 ),
              rownames = T, 
              selection = 'single',
              escape = F,
              filter = 'bottom',
              class = 'cell-border strip hover')
  })
```

