---
title: "BioRad Vertical Profiles"
output: 
    flexdashboard::flex_dashboard:
      vertical_layout: scroll
      orientation: rows
      theme: yeti
social: menu
source_code: embed
runtime: shiny
---
    
```{r global, include=FALSE}

# load data in 'global' chunk so it can be shared by all users of the dashboard
source('lib/initialize.R')
station_choices <- read_csv(here('nexrad_station_info/nexrad-stations.csv'))
bioRad::check_docker()


```

Instructions
=======================================================================

### Welcome
This is a flexDashboard that was built around the BioRad package's `calculate_vp()` function. It's purpose is to take some of the hassle and potential for error out of the process by replacing code inputs with a graphical user interface. 

Documentation for the function may be found here:

* https://rdrr.io/cran/bioRad/man/calculate_vp.html


When you are ready to begin, click the tab at the top labeled "Calculate Vertical Profiles."

Once there, select a NEXRAD station from the available choices to the left. Next, select the date that you are interested in. A drop down list will show the available NEXRAD files for the selected station and date. Select a file and click "Calculate Vertical Profile"

Tabs will populate to the right with a plot and tabular information about the selected date and time. 

Calculate Vertical Profiles
=======================================================================

Inputs {.sidebar data-width=375}
-----------------------------------------------------------------------
    
```{r}
# Select NEXRAD Station
selectInput(inputId = 'nex_station', label = strong('Select NEXRAD Station:'), width = '100%',
              choices = station_choices %>% 
                select(ICAO) %>%
                distinct() %>% 
                deframe(),
              selected = 'KFWS')
# Select Date
dateInput(inputId = 'date', label = strong('Select Date:'), width = '100%')

# Create a list of available NEXRAD files for selected station and date
available_files <- reactive({
    get_bucket_df(bucket = "noaa-nexrad-level2", 
                  key = "",
                  prefix = paste0(as.character(input$date, format="%Y/%m/%d"),"/", input$nex_station)
                  ) %>% 
        tibble()
    })
# Select NEXRAD file
renderUI({
    selectInput(inputId = 'nex_file', label = strong('Select from Available NEXRAD Files:'), width = '100%',
            choices = available_files() %>% 
                deframe()
            )
         })

actionButton(inputId = 'action',label = 'Calculate Vertical Profile',icon = icon('satellite-dish'))

# observeEvent(input$action, {
#   updateTabsetPanel(session = session, inputId = 'tabs', selected = 'Vertical Profile')
# })

```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Vertical Profile

```{r, fig.height=10, fig.width=8}

# Download radar data and store vertical profile information as a reactive variable when button clicked
  my_vp <- eventReactive(input$action, {
    # Check to see if you already have the radar file, if so, use it
    if(file.exists(here('nexrad_data', input$nex_file)) == T) {
      # Using BioRad, calculate vertical profile
      calculate_vp(here('nexrad_data', input$nex_file),
                   h_layer = 300, 
                   dual_pol = T, 
                   dealias = T,
                   range_max = 35000,
                   sd_vvp_threshold = 1)
    } else {
    # If you don't already have the necessary file...
    # Save Radar Data File from AWS
      save_object(object = input$nex_file, bucket = "noaa-nexrad-level2", key = "", secret = "", region = "us-east-1",
                      file = here('nexrad_data', input$nex_file))
    # Using BioRad, calculate vertical profile
      calculate_vp(here('nexrad_data', input$nex_file),
                   h_layer = 300, 
                   dual_pol = T, 
                   dealias = T,
                   range_max = 35000,
                   sd_vvp_threshold = 1)
    }
      })
# Offer an option to save the plot
  # downloadButton(outputId = "savePlot",label = "Save Plot")
  downloadHandler(filename = function() {
    filename = paste0(basename(input$nex_file), ".png")
    },
    content = function(file) {
      png(file, width = 640, height = 480)
      plot(my_vp(), quantity = 'dbz',main = basename(input$nex_file)) 
      dev.off()
      }
    )
# Render the Vertical Profile
  miniContentPanel(
  renderPlot({
    req(my_vp() )
    plot(my_vp(), quantity = 'dbz',main = basename(input$nex_file)) 
    }, height = 750),
  scrollable = T
  )
```

### Tabular
```{r}
renderDataTable({
  req(my_vp())
  my_vp()$data %>% 
    datatable(extensions = list('Scroller' = NULL,'Buttons' = NULL),
              options = list(scrollX = TRUE,
                 deferRender = TRUE,
                 scrollY = '600px',
                 scroller = TRUE,
                 searchHighlight = TRUE, 
                 search = list(regex = TRUE, 
                               caseInsensitive = TRUE),
                 dom = 'Bfrtip',
                 buttons = list(list(extend = 'csv',
                                     filename = basename(input$nex_file)),
                                list(extend= 'excel',
                                     filename = basename(input$nex_file))
                                )
                 ),
              rownames = F, 
              selection = 'single',
              escape = F,
              filter = 'bottom',
              class = 'cell-border strip hover')
  })
```

